Not much time has passed after the planning until we already began looking for doctors who could cooperate with us on the project. \\
For this purpose we sought doctors who were active exclusively in the field of oncology. \\
The term oncology is reffered to the branch of medicine that deals with the diagnosis, treatment and prevention of different types of cancer (tumor disease). \\
With our project being almost entirely about breast mammography, we needed doctors which are specialized in the field of oncology, more specific - breast oncology.  
According to this categorization we then proceeded.\\
After some research on the internet and also in books, we finally cut down 26 doctors who could be considered qualified to for the project. \\
We have sent all of the doctors a brief description of our project. We explained to them the core and the content of the project. Some of them answered the e-mails we sent.  \\
Most of the doctors have too much research to do, thus they just don't have as much time. \\
We arranged a few appointments, which were unfortunately not in the time span of our project. \\
Two doctors sent us a study protocol request, which means they required a protocol of our project that is extremely detailed. \\
We wrote the following protocol and sendt it to the doctors. \\
This we sent the doctors. \\
Dr. Serafino Forte of the hospital of Baden has invited us to the hospital after examining the study protocol. \\
We talked to him about all the details in medical and organizational terms. At first he looked at our mammography record. Immediately he realized that our mammographys are obsolete, because this technology is no longer needed and probably outdated. \\
Our data was in the old format of the film-film system. This was good for our project on the one hand but on the other hand it didn't speak so good. \\
It is definitely an advantage, because we have the possibility to have different mammographys evaluated. \\
However, it has a disadvantage too. \\
It is very difficult to get to the new mammographys because we need a lot of mammographys to train our software, we have to submit an ethics application. \\
This is an even more detailed application than the study protocol, which is checking if our project is as trustworthy as possible. \\
The application is examined by the Swiss Ethics Committees for Human Research. \\
In this application the financial resources are examined. \\
The financial resources are checked because the application is not free of charge. \\
To submit an application, you have to pay a basic flat rate of 800.00 CHF. \\
A check should be made for how well can the people be put together.
This means that four individuals working as a team could possibly carry out such a project because at the end of it it's just a product, resulting from months of work. \\
Apart from the organizational, we have also looked at the medical aspects as mentioned earlier in the chapter. \\
For Dr. Serafino Forte, it was quite important that our software could not only tell you whether a person is diagnosed with cancer, but also what type of cancer does he have. \\
