We have used the following platforms and programs for the work  Visual Studio; LaTex; and Github.\\

\subsection {Visual Studio}

Visual Studio is a programming tool we have programmed all of our software in. We have worked with it quite a lot as well. Since Visual Studio is very modern, it didn't cause us problems and without a doubt helped us with the project changes that we made.\\
 Changes applied to the software structure were not too difficult.

\subsection {LaTex}

The tool we used for our documentation and design is LaTex, the advantages of which are that LaTex is platform-independent, which means one can use it on any device.\\
 Some rather special formulas can also be used, and the program formats it by itself so we don’t have to worry about it.

\subsection {Github}

Github is an online platform we used to store the code we have written in. In Github people can work on projects together and view other people's work. It can also work in a way that people give other people tasks or demand a review of a task. Github is and has been an enormous help to our project, beause it has given us an overview of the things we have programmed. On top of that, Github gives us reasssurement because every work has been checked and reviewed by some other member of the site. \\
In Github you can also make branches. A branch is a copy of a project. On one hand, it offers additional security for the programmer because if any changes are made in the original project, it can be possible that this would no longer works. On the other hand, if one is working on the branch, nothing can be destroyed. \\
Changes and edits in the branch can of course be made in the original project, but only if it's in order. Since our project was public on Github, people who had no idea about it, but were interested in it, could take a look at it. \\
Specialists in our area of expertise could look at our program and give us tips, for example on how to improve it. Github has many advantages and offers the user many possibilities.
